`phyr`: An R package for model-based phylogenetic analyses

### 2018-11-03 ms.Rmd
update pglmm [skip ci]

The original code for `communityPGLMM` were imported from the R package `pez` [@pearse2015pez]. Its theorectical background was presented in @ives2011generalized. We improved both the user interface and the speed of `communityPGLMM` here. Function `pez::communityPGLMM` requires user-prepared random terms while `phyr::communityPGLMM` makes this step much easier by adapting formula syntax for mixed models provided by the R package `lme4` [@bates2015lme4].

@@

>>>>

The original code for `communityPGLMM` were imported from the R package `pez` [@pearse2015pez]. Its theorectical background was presented in @ives2011generalized. We made several important updates here.

- First, function `pez::communityPGLMM` requires user-prepared random terms while `phyr::communityPGLMM` makes this step much easier by adapting formula syntax for mixed models provided by the R package `lme4` [@bates2015lme4]. To specify a random term with design matrix derived from a phylogenetic variance-covariance matrix, we can append two underscores (`__`) to the group variable. For example, `(1 | sp__)` will create *two* random terms: one with and one without (i.e. identity matrix) phylogenetic design matrix. To test whether closely related species are more or less likely to co-occur in the same site, we can use `(sp__@site)` along with the argument `repulsion = TRUE` (overdispersion) or `repulsion = FALSE` (underdispersion).
- Second, we extended `communityPGLMM` to work with Binomial and Poisson distributed data while `pez::communityPGLMM` only allows Binary and Gaussian data.
- Third, we provided both Maximum likelihood and Bayesian approaches to fit PGLMMs. Users can choose the approach via `bayes = TRUE` or `bayes = FALSE` (default). The Bayesian PGLMMs were fitted with integrated nested Laplace approximations [INLA, @rue2009approximate].
- Fourth, we improved the speed of `communityPGLMM` by rewriting key functions in c++.

@@

### Speed comparisons

A table to compare the speed of functions in `phyr` with their original versions.
